### 2021-04-21 paper/ase21/report/syntax.tex
[ASE21] Report: concrete semantics

    &&&&\mid&
    \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
    \vspace*{1em}
  \end{array}
\]

>>>>

    &&&&\mid&
    \tnum \mid \tbigint \mid \tstr \mid \tsymb \\
    \vspace*{1em}
  \end{array}
\]
A modified $\ires$ program $\prog = (\getfunc, \getinst, \getnext)$ consists of
three mappings;  $\getfunc: \labset \rightarrow \funcset$ maps labels to their
functions, $\getinst: \labset \rightarrow \instset$ maps labels to their
instructions, and $\getnext: \labset \rightarrow \labset$ maps labels to their
next labels, where a label $\lab \in \labset$ denotes a program point. A
function $\kwdef \; \f (\x^*, \kwsl \y^* \kwsr). \; \lab \in \funcset$ consists
of its name $\f$, normal parameters $\x^*$, optional parameters $\y^*$, and a
body label $\lab$.  For presentation brevity, we assume that no global variables
exist in this paper.  An instruction $\inst$ is a variable declaration, a
function call, an assertion, a branch, a return, or a reference update.  An
invocation of an abstract algorithm in ECMAScript is compiled to a function call
instruction with a new temporary variable.  We represent loops using branch
instructions with cyclic pointing of labels in $\getnext$.  A reference $\refer$
is a variable $\x$ or a field access $\refer \kwsl \expr \kwsr$.  We write
$\refer.\f$ to briefly represent $\refer \kwsl \code{"f"} \kwsr$. An expression
$\expr$ is a record, a list, a type check, an existence check, a binary
operation, a unary operation, a reference, a constant, or a primitive, which is
either $\undefval$, $\nullval$, a \jscode{Boolean} $\bool$, a \jscode{Number}
$\num$, a \jscode{BigInt} $\bigint$, a \jscode{String} $\str$, or a
\jscode{Symbol} $\symb$.

A type $\ty \in \tyset$ is either a nominal type $\tname$, an empty list type
$\clist{}$, a parametric list type $\clist{\ty}$, a JavaScript type $\tjs$, a
primitive type $\tprim$, a numeric type $\tnumeric$, $\tnum$, $\tbigint$,
$\tstr$, or $\tsymb$.  The subtype relation $\subtype \subseteq \tyset \times
\tyset$ between types is reflexive and transitive.
